---
title: "Flexible Dashboard"
output: 
  flexdashboard::flex_dashboard:
    navbar:
      - {title: "About", href: "https://naver.com", align: left}
      - {title: "Google", href: "https://google.com", align: right}
      - {title: "File", href: "C:/Users/Daniel/Documents/ipds_kr_R_book/ch10_Breast_Cancer_Predicting/ch10%20Breast%20Cancer%20Predicting.nb.html", align: right}
    social : ['twitter', 'facebook', 'menu']
    orientation: rows
    # vertical_layout: scroll
    source_code: embed
    vertical_layout: scroll
    theme: yeti
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
# install.packages('d3heatmap')
library(d3heatmap)
library(dygraphs)
library(plotly)
library(xts)
# install.packages('metricsgraphics')
library(metricsgraphics)
library(flexdashboard)
library(tidyverse)
library(plotly)
library(dygraphs)
library(DT)
library(gapminder)
library(gridExtra)
library(ggthemes)
```

Analysis {.storyboard}
======================================================================


### Leaflet is a JavaScript library for creating dynamic maps that support panning and zooming along with variou s annotations.

```{r}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addMarkers(lng=174.768, lat=-36.852, popup="The bith place of R")
```

***

https://rstudio.github.io/leaflet/

- Interactive panning / zooming

- Compose maps using arbitary combinations of map titles, markers, polygons, lines, popups, and GeoJSON.

- Create maps right from the R console or RStudio

- Embed maps in knitr/R Markdown documents and Shint apps

- Easily render Spatial objects from the sp package, or data frames with lattitude/longitude columns

- Use map bounds and mouse events to drive Shiny logic

### d3heatmap creates interactive D3 heatmaps including support for row/column highlighting and zooming.  {data-commentary-height=700}

```{r}
data("mtcars")
d3heatmap(mtcars[, -2], scale = 'column', colors="Blues")
```

*** 

https://github.com/rstudio/d3heatmap

- Highlight rows/columns by clicking axis labels

- Click and drag over colormap to zoom in (click on colormap to zoom out)

- Optional clustering and dendrograms, courtesy of base::heatmap

<br>

<br>

<br>

<br>

<br>

<br>

<br>

### Dygraphs provides rich facilities for charting time-series data in R and includes support for many interactive features.


```{r}
# data("sample_matrix")
# m <- tail(sample_matrix, n=32)
# 
# # cbind(m, apply(m[, 1:3], 1, mean))
# 
# m %>%
#   as.data.frame() %>%
#   row.names.data.frame() %>% enframe() %>%
#   rename(date = value) %>%
#   select(-name) -> date_df
# 
# m %>% as_tibble() -> m_df
# 
# date_df %>%
#   bind_cols(m_df) %>%
#   gather(variable, value, -c(date, Close)) %>%
#   group_by(date) %>%
#   summarise(mean.value = mean(value)) -> mean_df
# 
# date_df %>%
#   bind_cols(m_df) %>%
#   left_join(mean_df, by = 'date') %>%
#   mutate(date = as.Date(date, "%Y-%m-%d")) -> date_df_1
# 
# m <- xts(date_df_1[, -1], date_df_1[, 1], order.by = as.POSIXct(date_df_1$date))
# saveRDS(m, file = 'm.rds')

m <- readRDS('m.rds')

dygraph(m) %>%
  dyCandlestick()
```

***

https://rstudio.github.io/dygraphs/

- Automatically plots xts time series objects (or any object convertible to xts).

- Highly configurable axis and series display (including optional second Y-axis).

- Rich interactive features including zoom/pan and series/point highlighting.

- Display upper/lower bars (e.g. prediction intervals) around series.

- Various graph overlays including shaded regions, event lines, and point annotations.

- 주가 변화를 예측해 보면 다음 주 오를 전망입니다.


### Plotly provides bindings to the plotly.js library and allows you to easily translate your ggplot2 graphics into an interactive web-based version.

```{r}
library(plotly)
p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "dodge")
ggplotly(p)
```

***

https://plot.ly/ggplot2/

If you use ggplot2, `ggplotly()` converts your plots to an interactive, web-based version! It also provides sensible tooltips, which assists decoding of values encoded as visual properties in the plot.

plotly supports some chart types that ggplot2 doesn't (such as 3D surface, point, and line plots). You can create these (or any other plotly) charts using `plot_ly()`.

<br>

<br>

<br>


### MetricsGraphics enables easy creation of D3 scatterplots, line charts, and histograms.

```{r}
library(metricsgraphics)
mjs_plot(mtcars, x=wt, y=mpg) %>%
  mjs_point(color_accessor=carb, size_accessor=carb) %>%
  mjs_labs(x="Weight of Car", y="Miles per Gallon")
```

***

https://hrbrmstr.github.io/metricsgraphics/

Building metricsgraphics charts follows the “piping” idiom made popular through the magrittr, ggvis and dplyr packages. This makes it possible to avoid one giant function with a ton of parameters and facilitates breaking out the chart building into logical steps. 

While MetricsGraphics.js charts may not have the flexibility of ggplot2, you can build functional, interactive [multi-]line, scatterplot, bar charts & histograms and + even link charts together.

<br>

<br>

<br>


Page 1 {data-navmenu="Menu A"}
======================================================================

Monthly deaths from bronchitis, emphysema and asthma in the
UK, 1974–1979 (Source: P. J. Diggle, 1990, Time Series: A
Biostatistical Introduction. Oxford, table A.3)

```{r}

wdbc <- tbl_df(read.table('wdbc.data', strip.white = T, 
                          sep = ',', header = F))

feature_names <- c('radius', 'texture', 'perimeter', 'area', 'smoothness', 'compactness', 
                   'concavity', 'concave_points', 'symmetry', 'fractal_dim')

names(wdbc) <- c('id', 
                 'class', 
                 paste0('mean_', feature_names),
                 paste0('se_', feature_names),
                 paste0('worst_', feature_names))

```

Rows
-----------------------------------------------------------------------

### Articles per Day

```{r}
# articles <- computeArticles()
valueBox(42, icon= 'fa-pencil', href = "flexdash_1.html")
```

### Commnents per Day

```{r}
# comments <- computeComments()
valueBox(126, icon = 'glyphicon-comment')
```

### Spam per Day

```{r}
spam <- 5
valueBox(spam,
         icon = 'fa-trash')
```


Rows
-----------------------------------------------------------------------

### Chart 1 {.no-title .no-padding}

```{r}
cars %>%
  ggplot(aes(speed, dist)) +
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme_minimal() +
  xlab("Speed(mile/h)") +
  ylab("Distance(mile)") +
  ggtitle("Car Graph") -> p_car

ggplotly(p_car)
```

> With car speed dataset, the linear regression result.

### Chart 2 {.no-title data-padding=10}

```{r}
pressure %>%
  ggplot(aes(temperature, pressure)) + 
  geom_point() +
  geom_smooth(method = "gam") + 
  theme_minimal() +
  xlab("Temperature") +
  ylab("Pressure") +
  ggtitle("Pressure Graph") -> p_pressure

ggplotly(p_pressure)
``` 



Rows 
-----------------------------------------------------------------------

### Contact Rate

```{r}
rate <- 91

gauge(rate, min = 0, max = 100, symbol = '%',
      gaugeSectors(success = c(80, 100),
                   warning = c(40, 79),
                   danger = c(0, 39)
                   ))
```

### Average Rating

```{r}
rating <- 37.4

gauge(rating, min = 0, max = 50, 
      gaugeSectors(success = c(41, 50),
                   warning = c(21, 40),
                   danger = c(0, 20)
                   ))
```

### Cancellations

```{r}
cancellations <- 7

gauge(cancellations, min = 0, max = 50, 
      gaugeSectors(success = c(0, 2),
                   warning = c(3, 6),
                   danger = c(7, 10)
                   ), 
      href = 'flexdash_1.html')
```

### About dygraphs

This example makes use of the dygraphs R package. The dygraphs
package provides rich facilities for charting time-series data 
in R. You can use dygraphs at the R console, within R Markdown
documents, and within Shiny applications.


Page 2 {data-orientation=rows data-navmenu="Menu A"}
======================================================================

Rows 
-----------------------------------------------------------------------

### Chart E

```{r}
diamonds %>%
  sample_n(1000) %>%
  ggplot(aes(carat, price, col = clarity)) +
  geom_point() -> p_diamonds

ggplotly(p_diamonds)
```


### Chart F

```{r}
gapminder %>%
  filter(year == 2007) %>%
  ggplot(aes(gdpPercap, lifeExp)) +
  geom_point(aes(size = pop, col = continent)) +
  scale_x_log10() +
  ggtitle("Gapminder data for 2007") -> p_gapminder

ggplotly(p_gapminder)
```


Page 3 {data-orientation=columns data-icon="fa-list"}
======================================================================

Column
-----------------------------------------------------------------------

### Chart G

```{r}

custom_theme <- theme_tufte() +
  theme(legend.position = c(.9, .9),
           legend.title = element_text(face = 'italic', size = 12),
           axis.title = element_text(face = 'bold', size = 14))

wdbc %>%
  group_by(class) %>%
  count() %>% 
  ungroup() %>%
  ggplot(aes(class, n, fill = class)) + geom_bar(stat = 'identity') +
  scale_fill_manual(values = c('red', 'blue')) +
  custom_theme -> p1

ggplotly(p1)
```


### Chart H

```{r}
custom_theme <- theme_tufte() +
  theme(legend.position = c(.9, .9),
           legend.title = element_text(face = 'italic', size = 12),
           axis.title = element_text(face = 'bold', size = 14))

wdbc %>% ggplot(aes(class, mean_concave_points, col = class)) +
  geom_jitter(alpha = .5) +
  geom_boxplot(alpha = .3) +
  scale_color_manual(values = c('red', 'blue')) +
  custom_theme -> p2

ggplotly(p2)
```

Column
-----------------------------------------------------------------------

### Chart I

```{r}
custom_theme <- theme_tufte() +
  theme(legend.position = c(.9, .9),
           legend.title = element_text(face = 'italic', size = 12),
           axis.title = element_text(face = 'bold', size = 14))

wdbc %>% ggplot(aes(class, mean_radius, col = class)) +
  geom_jitter(alpha = .5) +
  geom_boxplot(alpha= .5) +
  scale_color_manual(values = c('red', 'blue')) +
  custom_theme -> p3

ggplotly(p3)
```


### Chart J

```{r}
custom_theme <- theme_tufte() +
  theme(legend.position = c(.9, .9),
           legend.title = element_text(face = 'italic', size = 12),
           axis.title = element_text(face = 'bold', size = 14))

wdbc %>%
  ggplot(aes(mean_concave_points, mean_radius, col = class)) +
  geom_jitter(alpha = .7) +
  geom_smooth(alpha = .5)  +
  scale_color_manual(values = c('red', 'blue')) +
  custom_theme -> p4

ggplotly(p4)
```


Page 4 {data-orientation=columns data-icon="fa-hashtag"}
===================================== 

```{r global, include=FALSE}
library(datasets)
data(faithful)
```

Column {.sidebar}
-----------------------------------------------------------------------

Waiting time between eruptions and the duration of the eruption for the
Old Faithful geyser in Yellowstone National Park, Wyoming, USA.

```{r}
selectInput("n_breaks", label = "Number of bins:",
            choices = c(10, 20, 35, 50), selected = 20)

sliderInput("bw_adjust", label = "Bandwidth adjustment:",
            min = 0.2, max = 2, value = 1, step = 0.2)
```

Column
-----------------------------------------------------------------------

### Geyser Eruption Duration

```{r}
renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser Eruption Duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```












